#II)


---
title: "script poverty report on Benin, Mali, Burkina Faso, Togo"
output: html_document
---
##This script performs poverty analysis using multiple indices for four different countries. It merges household and welfare data, defines functions to calculate poverty indices (FGT, Watts, Chakravarty), computes these indices for different subgroups, and compares poverty levels across these countries using stochastic dominance tests. The results are organized and stored for further analysis. It is a group work done during the third year of barchelor's degree in 2022/2023.

Benin

Data Importation: This code loads two datasets related to Benin in 2018 using the haven package and displays them. It then creates a table combining "Raw score," "Latent trait," and "Prevalence," with the latter calculated as the column sums of a specific variable (pp.mali$f). The table is assigned row names "Thres 1" and "Thres 2" and displayed.
```{r installation}
# Case of Benin
library(haven)
ehcvm_welfare_ben2018 <- read_dta("ehcvm_welfare_ben2018.dta") 
View(ehcvm_welfare_ben2018)
library(haven)
ehcvm_individu_ben2018 <- read_dta("ehcvm_individu_ben2018.dta")
View(ehcvm_individu_ben2018)

# Prevalence table with thresholds
tab = cbind("Raw score" = c(4, 7), "Latent trait" = pp.mali$thres, 
"Prevalence" = colSums(pp.mali$f))
rownames(tab) = c("Thres 1", "Thres 2")
tab


 
```


```{r definition-of-dataframes}
# Case of Benin
datw = ehcvm_welfare_ben2018
dati = ehcvm_individu_ben2018

datbn = merge(dati,datw[,c("hhid","zref","pcexp","hhsize","heduc","hdiploma","hage","hcsp","hgender","hbranch")], by="hhid")
View(datbn)

```

## construction of functions 

```{r definition-of-poverty-line}
lpa = function(datbn){ datbn$zref[1] }
```


```{r Creation-of-Foster-indices}

FGT = function(datbn,z,a) {
  
  y=datbn$pcexp
  w=datbn$hhweight
  z=datbn$zref
  
  round(sum((w*(1-y/z)^a)*(y<=z),na.rm = TRUE)*100/sum(w,na.rm = TRUE),2)
  
}
```

```{r Creation-of-Watts-indices}

Watts = function(datbn,z) {
  
  y=datbn$pcexp
  w=datbn$hhweight
  z=datbn$zref
  
   round(sum(w*log(z/y)*(y<=z))/sum(w),2)
   
}
```

```{r Creation-of-Chakravarty-indices}

Chakravarty = function(datbn,z,u) {
  
  y=datbn$pcexp
  w=datbn$hhweight
  z=datbn$zref
   resultat <- round(sum(w*(1-(y/z)^u)*(y<=z),na.rm = TRUE)*100/sum(w,na.rm = TRUE),2)
          return(resultat)
  
}
```

##Calculating Benin indices 

```{r National-level}

# Definition of a matrix to store the data
mat = matrix(0, ncol = 5, nrow = 1)

# Calculation of the indices
fgt = sapply(0:2, function(x) round(FGT(datbn, z, x), 2))
watts = round(Watts(datbn, z), 2)
chakravarty = round(Chakravarty(datbn, z, 0.5), 2)

mat[1, ] = c(fgt, watts, chakravarty)
ben_nat = data.frame(mat, check.names = TRUE)
names(ben_nat) <- c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
          
```

```{r At-the-life-level}

  # Create a list of unique values of the specified attribute
milieu_vals = sort(unique(datbn[["milieu"]]))

# Initialize a matrix to store the results
mat_mil = matrix(0, ncol = 5, nrow = length(milieu_vals))

# Loop over the attribute values to calculate the indices for each group
for (i in seq_along(milieu_vals)) {
  # Subset the data for the current attribute
  mil = subset(datbn, datbn[["milieu"]] == milieu_vals[i])
  
  # Calculate the indices for the subset of data
  fgt = sapply(0:2, function(x) round(FGT(mil, z, x), 2))
  watts = round(Watts(mil, z), 2)
  chakravarty = round(Chakravarty(mil, z, 0.5), 2)
  
  # Store the results in the matrix
  mat_mil[i, ] = c(fgt, watts, chakravarty)
}

ben_mil = data.frame(mat_mil, check.names = TRUE)
names(ben_mil) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r regions-level}

reg_vals = sort(unique(datbn[["region"]]))
mat_reg = matrix(0,ncol =5,nrow=length(reg_vals))

for (i in seq_along(reg_vals)) {
  
  reg = subset(datbn,datbn[["region"]]==reg_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT(reg, z, x), 2))
        watts= round(Watts(reg, z), 2)
        chakravarty =round(Chakravarty(reg, z, 0.5 ), 2)
        
  mat_reg[i,]= c(fgt, watts, chakravarty)
  
}

ben_reg = data.frame(mat_reg,check.names = TRUE)
names(ben_reg) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r sex-level}

sex_vals = sort(unique(datbn[["hgender"]]))
mat_sex = matrix(0,ncol =5,nrow=length(sex_vals))

for (i in seq_along(sex_vals)) {
  
  sex = subset(datbn,datbn[["hgender"]]==sex_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT(sex, z, x), 2))
        watts= round(Watts(sex, z), 2)
        chakravarty =round(Chakravarty(sex, z, 0.5 ), 2)
        
  mat_sex[i,]= c(fgt, watts, chakravarty)
  
}

ben_sex = data.frame(mat_sex,check.names = TRUE)
names(ben_sex) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r At-the-household-level}

men_vals = sort(unique(datbn[["hhsize"]]))
mat_men = matrix(0,ncol =5,nrow=length(men_vals))

for (i in seq_along(men_vals)) {
  
  men = subset(datbn,datbn[["hhsize"]]==men_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT(men, z, x), 2))
        watts= round(Watts(men, z), 2)
        chakravarty =round(Chakravarty(men, z, 0.5 ), 2)
        
  mat_men[i,]= c(fgt, watts, chakravarty)
  
}

ben_men = data.frame(mat_men,check.names = TRUE)
names(ben_men) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r education-level}

educ_vals = sort(unique(datbn[["heduc"]]))
mat_educ = matrix(0,ncol =5,nrow=length(educ_vals))

for (i in seq_along(educ_vals)) {
  
  educ = subset(datbn,datbn[["heduc"]]==educ_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT(educ, z, x), 2))
        watts= round(Watts(educ, z), 2)
        chakravarty =round(Chakravarty(educ, z, 0.5 ), 2)
        
  mat_educ[i,]= c(fgt, watts, chakravarty)
  
}

ben_educ = data.frame(mat_educ,check.names = TRUE)
names(ben_educ) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r sector-of-activity-level-of-CM}

bra_vals = sort(unique(datbn[["hbranch"]]))
mat_bra = matrix(0,ncol =5,nrow=length(bra_vals))

for (i in seq_along(bra_vals)) {
  
  bra = subset(datbn,datbn[["hbranch"]]==bra_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT(bra, z, x), 2))
        watts= round(Watts(bra, z), 2)
        chakravarty =round(Chakravarty(bra, z, 0.5 ), 2)
        
  mat_bra[i,]= c(fgt, watts, chakravarty)
  
}

ben_bra= data.frame(mat_bra,check.names = TRUE)
names(ben_bra) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r age-level-of-CM}

age_vals = sort(unique(datbn[["hage"]]))
mat_age = matrix(0,ncol =5,nrow=length(age_vals))

for (i in seq_along(age_vals)) {
  
  age = subset(datbn,datbn[["hage"]]==age_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT(age, z, x), 2))
        watts= round(Watts(bra, z), 2)
        chakravarty =round(Chakravarty(age, z, 0.5 ), 2)
        
  mat_age[i,]= c(fgt, watts, chakravarty)
  
  
}

ben_age= data.frame(mat_age,check.names = TRUE)
names(ben_age) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")


```

# Burkina Faso 

```{r importing-dataset}
library(haven)
ehcvm_individu_bfa2018 <- read_sav("BURKINA /ehcvm_individu_bfa2018.sav")
View(ehcvm_individu_bfa2018)

ehcvm_welfare_bfa2018 <- read_sav("BURKINA /ehcvm_welfare_bfa2018.sav")
View(ehcvm_welfare_bfa2018)


```

```{r definition-of-dataframe}

datwbfa = ehcvm_welfare_bfa2018
datibfa  = ehcvm_individu_bfa2018

datbfa = merge(datibfa,datwbfa[,c("hhid","zref","pcexp","hhsize","heduc","hdiploma","hage","hcsp","hgender","hbranch")],by="hhid")

```
## defining functions for burkina 

```{r Foster-indices}
FGT_bfa = function(datbfa,z,a) {
  
  y=datbfa$pcexp
  w=datbfa$hhweight
  z=datbfa$zref
  
  round(sum((w*(1-y/z)^a)*(y<=z),na.rm = TRUE)*100/sum(w,na.rm = TRUE),2)
  
}

```

```{r Watts }
Watts_bfa = function(datbfa,z) 
  
{
  
  y=datbfa$pcexp
  w=datbfa$hhweight
  z=datbfa$zref
  
   round(sum(w*log(z/y)*(y<=z))/sum(w),2)
}

```

```{r Chakravarty}

Chakravarty_bfa = function(datbfa,z,u) 
  
{
  
  y=datbfa$pcexp
  w=datbfa$hhweight
  z=datbfa$zref
 resultat =  round(sum(w*(1-(y/z)^u)*(y<=z),na.rm = TRUE)*100/sum(w,na.rm = TRUE),2)
          return(resultat)
}

```

## calculing  indices 

```{r national-level-2}


matbfa = matrix(0,ncol=5,nrow=1)

fgt = sapply(0:2,function(x) round(FGT_bfa(datbfa,z,x),2))
watts = round(Watts_bfa(datbfa,z),2)
chakravarty = round(Chakravarty_bfa(datbfa,z,0.5),2)

matbfa[1,] = c(fgt,watts,chakravarty)
bfa_nat = data.frame(matbfa,check.names =TRUE)
names(bfa_nat) <- c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r life-level}

milieubfa_vals = sort(unique(datbfa[["milieu"]]))
mat_milbfa= matrix(0, ncol = 5, nrow = length(milieubfa_vals))
        
for (i in seq_along(milieubfa_vals)) {
         
 milbfa =  subset(datbfa, datbfa[["milieu"]] == milieubfa_vals[i])
          
      fgt = sapply(0:2, function(x) round(FGT_bfa(milbfa, z, x), 2))
      watts= round(Watts_bfa(milbfa, z), 2)
      chakravarty =round(Chakravarty_bfa(milbfa, z, 0.5 ), 2)
      
       mat_milbfa[i, ] = c(fgt, watts, chakravarty)
          
        }

  bfa_mil = data.frame(mat_milbfa,check.names = TRUE)
  names(bfa_mil) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r region-level}

regbfa_vals = sort(unique(datbfa[["region"]]))
mat_regbfa = matrix(0,ncol =5,nrow=length(regbfa_vals))

for (i in seq_along(regbfa_vals)) {
  
  regbfa = subset(datbfa,datbfa[["region"]]==regbfa_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_bfa(regbfa, z, x), 2))
        watts= round(Watts_bfa(regbfa, z), 2)
        chakravarty =round(Chakravarty_bfa(regbfa, z, 0.5 ), 2)
        
  mat_regbfa[i,]= c(fgt, watts, chakravarty)
  
}

bfa_reg = data.frame(mat_regbfa,check.names = TRUE)
names(bfa_reg) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r sex-level-2}

sexbfa_vals = sort(unique(datbfa[["hgender"]]))
mat_sexbfa = matrix(0,ncol =5,nrow=length(sexbfa_vals))

for (i in seq_along(sexbfa_vals)) {
  
  sexbfa = subset(datbfa,datbfa[["hgender"]]==sexbfa_vals[i])

        fgt = sapply(0:2, function(x) round(FGT_bfa(sexbfa, z, x), 2))
        watts= round(Watts_bfa(sexbfa, z), 2)
        chakravarty =round(Chakravarty_bfa(sexbfa, z, 0.5 ), 2)
        
  mat_sexbfa[i,]= c(fgt, watts, chakravarty)
  
}

bfa_sex = data.frame(mat_sexbfa,check.names = TRUE)
names(bfa_sex) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r house-hold-level}

menbfa_vals = sort(unique(datbfa[["hhsize"]]))
mat_menbfa = matrix(0,ncol =5,nrow=length(menbfa_vals))

for (i in seq_along(menbfa_vals)) {
  
  menbfa = subset(datbfa,datbfa[["hhsize"]]==menbfa_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_bfa(menbfa, z, x), 2))
        watts= round(Watts_bfa(menbfa, z), 2)
        chakravarty =round(Chakravarty_bfa(menbfa, z, 0.5 ), 2)
        
  mat_menbfa[i,]= c(fgt, watts, chakravarty)
  
}

bfa_men = data.frame(mat_menbfa,check.names = TRUE)
names(bfa_men) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
```

```{r education-level-2}
educbfa_vals = sort(unique(datbfa[["heduc"]]))
mat_educbfa = matrix(0,ncol =5,nrow=length(educbfa_vals))

for (i in seq_along(educbfa_vals)) {
  
  educbfa = subset(datbfa,datbfa[["heduc"]]==educbfa_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_bfa(educbfa, z, x), 2))
        watts= round(Watts_bfa(educbfa, z), 2)
        chakravarty =round(Chakravarty_bfa(educbfa, z, 0.5 ), 2)
        
  mat_educbfa[i,]= c(fgt, watts, chakravarty)
  
}

bfa_educ = data.frame(mat_educbfa,check.names = TRUE)
names(bfa_educ) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
```

```{r branche-of-activity}

brabfa_vals = sort(unique(datbfa[["hbranch"]]))
mat_brabfa = matrix(0,ncol =5,nrow=length(brabfa_vals))

for (i in seq_along(brabfa_vals)) {
  
  brabfa = subset(datbfa,datbfa[["hbranch"]]==brabfa_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_bfa(brabfa, z, x), 2))
        watts= round(Watts_bfa(brabfa, z), 2)
        chakravarty =round(Chakravarty_bfa(brabfa, z, 0.5 ), 2)
        
  mat_brabfa[i,]= c(fgt, watts, chakravarty)
  
}

bfa_bra= data.frame(mat_brabfa,check.names = TRUE)
names(bfa_bra) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
```

```{r age-level-of-CM-2}

agebfa_vals = sort(unique(datbfa[["hage"]]))
matbfa_age = matrix(0,ncol =5,nrow=length(agebfa_vals))

for (i in seq_along(agebfa_vals)) {
  
  agebfa = subset(datbfa,datbfa[["hage"]]==agebfa_vals[i])

        fgt = sapply(0:2, function(x) round(FGT_bfa(agebfa, z, x), 2))
        watts= round(Watts_bfa(agebfa, z), 2)
        chakravarty =round(Chakravarty_bfa(agebfa, z, 0.5 ), 2)
        
  matbfa_age[i,]= c(fgt, watts, chakravarty)
  
  
}

bfa_age = data.frame(matbfa_age,check.names = TRUE)
names(bfa_age) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
```

# Niger 


```{r importing-dataset-2}

ehcvm_welfare_ner2018 <- read_dta("nigr /ehcvm_welfare_ner2018.dta")
View(ehcvm_welfare_ner2018)

ehcvm_individu_ner2018 <- read_dta("nigr /ehcvm_individu_ner2018.dta")
View(ehcvm_individu_ner2018)

```

```{r definition-of-dataframe-2}

datwn = ehcvm_welfare_ner2018
datin  = ehcvm_individu_ner2018

datnig = merge(datin,datwn[,c("hhid","zref","pcexp","hhsize","heduc","hdiploma","hage","hcsp","hgender","hbranch")],by="hhid")

```

## definition of functions 

```{r definting-poverty-line}

lpan = function(datnig){ datnig$zref[1] }
```

```{r Foster-indices-2}

FGT_n = function(datnig,z,a) {
  
  y=datnig$pcexp
  w=datnig$hhweight
  z=datnig$zref
  
  round(sum((w*(1-y/z)^a)*(y<=z),na.rm = TRUE)*100/sum(w,na.rm = TRUE),2)
  
}
```

```{r Watts-2}
Watts_n = function(datnig,z) {
  
  y=datnig$pcexp
  w=datnig$hhweight
  z=datnig$zref
  
   round(sum(w*log(z/y)*(y<=z))/sum(w),2)
   
}

```

```{r Chakravarty-2}

Chakravarty_n = function(datnig,z,u) {
  
  y=datnig$pcexp
  w=datnig$hhweight
  z=datnig$zref
 resultat =  round(sum(w*(1-(y/z)^u)*(y<=z),na.rm = TRUE)*100/sum(w,na.rm = TRUE),2)
          return(resultat)
  
}

```

## calculating indices 

```{r national-level-3}
# Definition of a matrix to store the data 
matn = matrix(0, ncol=5, nrow=1)

# Calculation of indices 
fgt = sapply(0:2, function(x) round(FGT_n(datnig, z, x), 2))
watts = round(Watts_n(datnig, z), 2)
chakravarty = round(Chakravarty_n(datnig, z, 0.5), 2)

matn[1,] = c(fgt, watts, chakravarty)
nig_nat = data.frame(matn, check.names = TRUE)
names(nig_nat) <- c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r living-environment}

# Create a list of unique values for the specified attribute
milieun_vals = sort(unique(datnig[["milieu"]]))

# Initialize a matrix to store the results
mat_miln = matrix(0, ncol = 5, nrow = length(milieun_vals))

# Loop over the attribute values to calculate indices for each group
for (i in seq_along(milieun_vals)) {
  # Subset of data for the current attribute
  miln = subset(datnig, datnig[["milieu"]] == milieun_vals[i])
  
  # Calculate indices for the data subset
  fgt = sapply(0:2, function(x) round(FGT_n(miln, z, x), 2))
  watts = round(Watts_n(miln, z), 2)
  chakravarty = round(Chakravarty_n(miln, z, 0.5), 2)
  
  # Store the results in the matrix
  mat_miln[i, ] = c(fgt, watts, chakravarty)
}

# Create a data frame for the results
nig_mil = data.frame(mat_miln, check.names = TRUE)
names(nig_mil) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
   
```

```{r region-level-2}

regn_vals = sort(unique(datnig[["region"]]))
mat_regn = matrix(0,ncol =5,nrow=length(regn_vals))

for (i in seq_along(regn_vals)) {
  
  regn = subset(datnig,datnig[["region"]]==regn_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_n(regn, z, x), 2))
        watts= round(Watts_n(regn, z), 2)
        chakravarty =round(Chakravarty_n(regn, z, 0.5 ), 2)
        
  mat_regn[i,]= c(fgt, watts, chakravarty)
  
}

nig_reg = data.frame(mat_regn,check.names = TRUE)
names(nig_reg) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r sex-level-3}

sexn_vals = sort(unique(datnig[["hgender"]]))
mat_sexn = matrix(0,ncol =5,nrow=length(sexn_vals))

for (i in seq_along(sexn_vals)) {
  
  sexn = subset(datnig,datnig[["hgender"]]==sexn_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_n(sexn, z, x), 2))
        watts= round(Watts_n(sexn, z), 2)
        chakravarty =round(Chakravarty_n(sexn, z, 0.5 ), 2)
        
  mat_sexn[i,]= c(fgt, watts, chakravarty)
  
}

nig_sex = data.frame(mat_sexn,check.names = TRUE)
names(nig_sex) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r Household-size}

menn_vals = sort(unique(datnig[["hhsize"]]))
mat_menn = matrix(0,ncol =5,nrow=length(menn_vals))

for (i in seq_along(menn_vals)) {
  
  menn = subset(datnig,datnig[["hhsize"]]==menn_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_n(menn, z, x), 2))
        watts= round(Watts_n(menn, z), 2)
        chakravarty =round(Chakravarty_n(menn, z, 0.5 ), 2)
        
  mat_menn[i,]= c(fgt, watts, chakravarty)
  
}

nig_men = data.frame(mat_menn,check.names = TRUE)
names(nig_men) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r education-level-3}

educn_vals = sort(unique(datnig[["heduc"]]))
mat_educn = matrix(0,ncol =5,nrow=length(educn_vals))

for (i in seq_along(educn_vals)) {
  
  educn = subset(datnig,datnig[["heduc"]]==educn_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_n(educn, z, x), 2))
        watts= round(Watts_n(educn, z), 2)
        chakravarty =round(Chakravarty_n(educn, z, 0.5 ), 2)
        
  mat_educn[i,]= c(fgt, watts, chakravarty)
  
}

nig_educ = data.frame(mat_educn,check.names = TRUE)
names(nig_educ) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
```

```{r branche-of-d-activity}

bran_vals = sort(unique(datnig[["hbranch"]]))
mat_bran = matrix(0,ncol =5,nrow=length(bran_vals))

for (i in seq_along(bran_vals)) {
  
  bran = subset(datnig,datnig[["hbranch"]]==bran_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_n(bran, z, x), 2))
        watts= round(Watts_n(bran, z), 2)
        chakravarty =round(Chakravarty_n(bran, z, 0.5 ), 2)
        
  mat_bran[i,]= c(fgt, watts, chakravarty)
  
}

nig_bra= data.frame(mat_bran,check.names = TRUE)
names(nig_bra) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
```

```{r age-level}

agen_vals = sort(unique(datnig[["hage"]]))
matn_age = matrix(0,ncol =5,nrow=length(agen_vals))

for (i in seq_along(agen_vals)) {
  
  agen = subset(datnig,datnig[["hage"]]==agen_vals[i])

        fgt = sapply(0:2, function(x) round(FGT_n(agen, z, x), 2))
        watts= round(Watts_n(agen, z), 2)
        chakravarty =round(Chakravarty_n(agen, z, 0.5 ), 2)
        
  matn_age[i,]= c(fgt, watts, chakravarty)
  
  
}

nig_age= data.frame(matn_age,check.names = TRUE)
names(nig_age) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")



```

# Togo 

 
```{r importing-dataset-3}

ehcvm_welfare_tgo2018 <- read_dta("TOGO /ehcvm_welfare_tgo2018.dta")
View(ehcvm_welfare_tgo2018)
ehcvm_individu_tgo2018 <- read_dta("TOGO /ehcvm_individu_tgo2018.dta")
View(ehcvm_individu_tgo2018)

```

```{r creation-of-dataframe}

datwtgo = ehcvm_welfare_tgo2018
datitgo  = ehcvm_individu_tgo2018

dattgo = merge(datitgo,datwtgo[,c("hhid","zref","pcexp","hhsize","heduc","hdiploma","hage","hcsp","hgender","hbranch")],by="hhid")

```
## définition des fonctions pour le togo

```{r FOSTER-indices-3}

FGT_tgo = function(dattgo,z,a) {
  
  y=dattgo$pcexp
  w=dattgo$hhweight
  z=dattgo$zref
  
  round(sum((w*(1-y/z)^a)*(y<=z),na.rm = TRUE)*100/sum(w,na.rm = TRUE),2)
  
}

```

```{r Watts-3}

Watts_tgo = function(dattgo,z) 
  
{
  
  y=dattgo$pcexp
  w=dattgo$hhweight
  z=dattgo$zref
  
   round(sum(w*log(z/y)*(y<=z))/sum(w),2)
}

```

```{r Chakravarty-3}
Chakravarty_tgo = function(dattgo,z,u) 
  
{
  
  y=dattgo$pcexp
  w=dattgo$hhweight
  z=dattgo$zref
 resultat =  round(sum(w*(1-(y/z)^u)*(y<=z),na.rm = TRUE)*100/sum(w,na.rm = TRUE),2)
          return(resultat)
}

```

## calculating  indices 

```{r national-levell}

mattgo = matrix(0,ncol=5,nrow=1)

fgt = sapply(0:2,function(x) round(FGT_tgo(dattgo,z,x),2))
watts = round(Watts_tgo(dattgo,z),2)
chakravarty = round(Chakravarty_tgo(dattgo,z,0.5),2)

mattgo[1,] = c(fgt,watts,chakravarty)
tgo_nat = data.frame(mattgo,check.names =TRUE)
names(tgo_nat) <- c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
```

```{r life-enviroment}

milieutgo_vals = sort(unique(dattgo[["milieu"]]))
mat_miltgo= matrix(0, ncol = 5, nrow = length(milieutgo_vals))
        
for (i in seq_along(milieutgo_vals)) {
         
 miltgo =  subset(dattgo, dattgo[["milieu"]] == milieutgo_vals[i])
          
      fgt = sapply(0:2, function(x) round(FGT_tgo(miltgo, z, x), 2))
      watts= round(Watts_tgo(miltgo, z), 2)
      chakravarty =round(Chakravarty_tgo(miltgo, z, 0.5 ), 2)
      
       mat_miltgo[i, ] = c(fgt, watts, chakravarty)
          
        }

  tgo_mil = data.frame(mat_miltgo,check.names = TRUE)
  names(tgo_mil) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
```

```{r region-level-3}

regtgo_vals = sort(unique(dattgo[["region"]]))
mat_regtgo = matrix(0,ncol =5,nrow=length(regtgo_vals))

for (i in seq_along(regtgo_vals)) {
  
  regtgo = subset(dattgo,dattgo[["region"]]==regtgo_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_tgo(regtgo, z, x), 2))
        watts= round(Watts_tgo(regtgo, z), 2)
        chakravarty =round(Chakravarty_tgo(regtgo, z, 0.5 ), 2)
        
  mat_regtgo[i,]= c(fgt, watts, chakravarty)
  
}

tgo_reg = data.frame(mat_regtgo,check.names = TRUE)
names(tgo_reg) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
```

```{r sex-level-4}

sextgo_vals = sort(unique(dattgo[["hgender"]]))
mat_sextgo = matrix(0,ncol =5,nrow=length(sextgo_vals))

for (i in seq_along(sextgo_vals)) {
  
  sextgo = subset(dattgo,dattgo[["hgender"]]==sextgo_vals[i])

        fgt = sapply(0:2, function(x) round(FGT_tgo(sextgo, z, x), 2))
        watts= round(Watts_tgo(sextgo, z), 2)
        chakravarty =round(Chakravarty_tgo(sextgo, z, 0.5 ), 2)
        
  mat_sextgo[i,]= c(fgt, watts, chakravarty)
  
}

tgo_sex = data.frame(mat_sextgo,check.names = TRUE)
names(tgo_sex) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```

```{r household-level}

mentgo_vals = sort(unique(dattgo[["hhsize"]]))
mat_mentgo = matrix(0,ncol =5,nrow=length(mentgo_vals))

for (i in seq_along(mentgo_vals)) {
  
  mentgo = subset(dattgo,dattgo[["hhsize"]]==mentgo_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_tgo(mentgo, z, x), 2))
        watts= round(Watts_tgo(mentgo, z), 2)
        chakravarty =round(Chakravarty_tgo(mentgo, z, 0.5 ), 2)
        
  mat_mentgo[i,]= c(fgt, watts, chakravarty)
  
}

tgo_men = data.frame(mat_mentgo,check.names = TRUE)
names(tgo_men) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
```

```{r education-level-4}
eductgo_vals = sort(unique(dattgo[["heduc"]]))
mat_eductgo = matrix(0,ncol =5,nrow=length(eductgo_vals))

for (i in seq_along(eductgo_vals)) {
  
  eductgo = subset(dattgo,dattgo[["heduc"]]==eductgo_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_tgo(eductgo, z, x), 2))
        watts= round(Watts_tgo(eductgo, z), 2)
        chakravarty =round(Chakravarty_tgo(eductgo, z, 0.5 ), 2)
        
  mat_eductgo[i,]= c(fgt, watts, chakravarty)
  
}

tgo_educ = data.frame(mat_eductgo,check.names = TRUE)
names(tgo_educ) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
```

```{r branche-of-activite}

bratgo_vals = sort(unique(dattgo[["hbranch"]]))
mat_bratgo = matrix(0,ncol =5,nrow=length(bratgo_vals))

for (i in seq_along(bratgo_vals)) {
  
  bratgo = subset(dattgo,dattgo[["hbranch"]]==bratgo_vals[i])
  
        fgt = sapply(0:2, function(x) round(FGT_tgo(bratgo, z, x), 2))
        watts= round(Watts_tgo(bratgo, z), 2)
        chakravarty =round(Chakravarty_tgo(bratgo, z, 0.5 ), 2)
        
  mat_bratgo[i,]= c(fgt, watts, chakravarty)
  
}

tgo_bra= data.frame(mat_bratgo,check.names = TRUE)
names(tgo_bra) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")
```

```{r age-level-of-CM-3}

agetgo_vals = sort(unique(dattgo[["hage"]]))
mattgo_age = matrix(0,ncol =5,nrow=length(agetgo_vals))

for (i in seq_along(agetgo_vals)) {
  
  agetgo = subset(dattgo,dattgo[["hage"]]==agetgo_vals[i])

        fgt = sapply(0:2, function(x) round(FGT_tgo(agetgo, z, x), 2))
        watts= round(Watts_tgo(agetgo, z), 2)
        chakravarty =round(Chakravarty_tgo(agetgo, z, 0.5 ), 2)
        
  mattgo_age[i,]= c(fgt, watts, chakravarty)
  
  
}

tgo_age = data.frame(mattgo_age,check.names = TRUE)
names(tgo_age) = c("Incidence", "Depth", "Severity", "Watts", "Chakravarty")

```
#Stochastic dominance


```{r Stochastic-dominance-at-national}
# Definition of poverty thresholds
zben = 246542
zbfa = 194629
znig = 181782
ztgo = 273618

# Creation of poverty line vectors
vz_ben = sort(unique(datbn$pcexp[datbn$pcexp <= zben]))
vz_bfa = sort(unique(datbfa$pcexp[datbfa$pcexp <= zbfa]))
vz_nig = sort(unique(datnig$pcexp[datnig$pcexp <= znig]))
vz_tgo = sort(unique(dattgo$pcexp[dattgo$pcexp <= ztgo]))

# Functions for poverty measures (FGT)
res.dom.ben = with(datbn, sapply(datbn, FGT, z = vz_ben, y = pcexp, a = 0))

a = c(1, 2, 3, 4)
combn(a, 2)
AZ = NA
AZ = combn(a, 2)[1, ] - combn(a, 2)[2, ]
AZ
ifelse(AZ[1] <= 0, AZ, NA)

# (Replace 'a' with a vector of the 4 poverty measures functions)
AZ[1] >= 0
                                
```

```{r}
# Define the function Ft to calculate the poverty gap index using a specific formula based on household weights, income (y), and poverty thresholds (z) for each country. 
Ft = function(y, z, w, a) {
  y   # Poverty line for each country
  w   # Household weights
  z   # Poverty threshold
  # Calculate the poverty gap index with the formula and round the result
  round(sum((w * (1 - y / z)^a) * (y <= z), na.rm = TRUE) * 100 / sum(w, na.rm = TRUE), 2)
}

# Apply the Ft function to the data of each country (Benin, Burkina Faso, Niger, and Togo) with the corresponding poverty line (vz_ben, vz_bfa, etc.)
res.dom.ben = with(datbn, sapply(vz_ben, Ft, y = datbn$pcexp, w = datbn$hhweight, a = 0))
res.dom.bfa = with(datbfa, sapply(vz_bfa, Ft, y = datbfa$pcexp, w = datbfa$hhweight, a = 0))
res.dom.nig = with(datnig, sapply(vz_nig, Ft, y = datnig$pcexp, w = datnig$hhweight, a = 0))
res.dom.tgo = with(dattgo, sapply(vz_tgo, Ft, y = dattgo$pcexp, w = dattgo$hhweight, a = 0))

# Calculate the differences between poverty measures for different country pairs and check if the first country dominates the second (i.e., has lower poverty)
ERR = res.dom.ben - res.dom.bfa
all(ERR <= 0)  # Check if Benin dominates Burkina Faso

# Create a matrix for dominance comparison between countries
g = matrix(data = (c(1, 2, 3, 4)), ncol = 4, nrow = 4, byrow = TRUE)

# Initialize empty vectors to store dominance comparison results for each country pair
bfa.val = c("bfa-ben" = NA, "bfa-nig" = NA, "bfa-tgo" = NA)
nig.val = c("nig-ben" = NA, "nig-bfa" = NA, "nig-tgo" = NA)
tgo.val = c("tgo-ben" = NA, "tgo-bfa" = NA, "tgo-nig" = NA)

# Compare Benin to other countries
abb = res.dom.ben - res.dom.bfa
ab = all(abb <= 0)
acc = res.dom.ben - res.dom.nig
ac = all(acc <= 0)
add = res.dom.ben - res.dom.tgo
ad = all(add <= 0)
ben.val = c(ab, ac, ad)

# Compare Burkina Faso to other countries
baa = res.dom.bfa - res.dom.ben
ba = all(baa <= 0)
bcc = res.dom.bfa - res.dom.nig
bc = all(bcc <= 0)
bdd = res.dom.bfa - res.dom.tgo
bd = all(bdd <= 0)
bfa.val = c(ba, bc, bd)

# Compare Niger to other countries
caa = res.dom.nig - res.dom.ben
ca = all(caa <= 0)
cbb = res.dom.nig - res.dom.bfa
cb = all(cbb <= 0)
cdd = res.dom.nig - res.dom.tgo
cd = all(cdd <= 0)
nig.val = c(ca, cb, cd)

# Compare Togo to other countries
daa = res.dom.tgo - res.dom.ben
da = all(daa <= 0)
dbb = res.dom.tgo - res.dom.bfa
db = all(dbb <= 0)
dcc = res.dom.tgo - res.dom.nig
dc = all(dcc <= 0)
tgo.val = c(da, db, dc)

# Store the results of dominance comparisons in a vector and create a matrix of the results
dominance.stoch = c(ben.val, bfa.val, nig.val, tgo.val)
mat.dom = matrix(dominance.stoch, ncol = 3, nrow = 4, byrow = TRUE)
mat.dom

# Check if the dominance comparisons for Benin are valid (all TRUE)
BEN.dom = c(ab1, ac1, ad1)
BEN.dom
BEN.dom >= 0
BEN.dom == "TRUE"

# Loop through a list of poverty measure results for different countries and perform additional analysis (though incomplete here)
for (i in length(c(res.dom.bfa, res.dom.nig, res.dom.tgo))) {
  res.dom.ben - i
  MAT = c
}

# Summarize the poverty data for Benin (datbn$pcexp)
summary(datbn$pcexp)

# Create combinations of elements in a vector D and calculate their differences
combn(D, 2)
length
AZ = NA
AZ = combn(D, 2)[1, ] - combn(D, 2)[2, ]
AZ

AZ.bis = NA
AZ.bis = combn(D, 2)[2, ] - combn(D, 2)[1, ]
AZ.bis

# Create combinations of the numbers 1, 2, 3, and 4 taken 2 at a time
combn(c(1, 2, 3, 4), 2)

# Define a function to calculate the FGT poverty measure for a specific threshold z and parameter a
FGTy = function(datbn, z, a) {
  y = datbfa$pcexp  # Income
  w = datbfa$hhweight  # Household weights
  z = 267985  # Poverty threshold
  # Calculate the FGT measure
  round(sum((w * (1 - y / z)^a) * (y <= z), na.rm = TRUE) * 100 / sum(w, na.rm = TRUE), 2)
}

# Apply the FGT function for different values of a (0, 1, and 2)
fgty = sapply(0:2, function(x) round(FGTy(datbfa, z, x), 2))

```

